Marker imputation efficiency for Genotyping-By-Sequencing data of crop species with and without a reference genome \thanks{Nelson Nazzicari and Filippo Biscarini contributed equally to the work \\ Corresponding author: Nelson Nazzicari \email{nelson.nazzicari@crea.gov.it}}

### 2016-05-04 Nazzicari_Imputation_suppl.tex
supplementary in joint file

\section{Supplementary material}
\label{sec:supplementary_material}

@@

\subsection{Supplementary tables}
\label{sec:supplementary_tables}
\input{inputs/table_accuracies.tex}

@@

>>>>

\begin{filecontents*}{example.eps}
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
\RequirePackage{fix-cm}
\documentclass[smallextended]{svjour3}       \smartqed  
\usepackage{xfrac}   
\usepackage{lineno}  
\usepackage{graphicx}
\usepackage{color}
\usepackage{multirow}
\usepackage{array}
\usepackage{setspace} 
\usepackage{makecell}
\usepackage{amsmath}

\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\renewcommand{\figurename}{Suppl. Fig.}
\renewcommand{\tablename}{Suppl. Table}

\linenumbers
\doublespacing 
\journalname{Molecular Breeding}
\begin{document}

\title{
Marker imputation efficiency for Genotyping-By-Sequencing data of crop species with and without a reference genome 
\thanks{Nelson Nazzicari and Filippo Biscarini contributed equally to the work \\
Corresponding author: Nelson Nazzicari \email{nelson.nazzicari@crea.gov.it}}
}

\titlerunning{Imputation efficiency for GBS data with and without the reference genome}

\author{Nelson Nazzicari \and
  Filippo Biscarini  \and
  Paolo Cozzi \and
  E. Charles Brummer \and
  Paolo Annicchiarico
}

\authorrunning{Nazzicari, Biscarini et al.} 
\institute{
    N. Nazzicari, P. Annicchiarico \at Council for Agricultural Research and Economics (CREA) Research Centre for Fodder Crops and Dairy Productions, Lodi (Italy)
\and
    F. Biscarini, P. Cozzi \at Dipartimento di Bioinformatica, Fondazione Parco Tecnologico Padano, Lodi (Italy)
\and
    E.C. Brummer \at University of California, Plant Sciences Department, Davis, CA (USA)
}

\date{Received:  / Accepted:}

\maketitle

\graphicspath{{./figures/}}
\makeatletter{}\section{Supplementary material}
\label{sec:supplementary_material}

@@

\subsection{Supplementary tables}
\label{sec:supplementary_tables}
\makeatletter{}\begin{table}
\centering
\caption[Accuracy statistics]{Imputation accuracies (as percentages) for the various
datasets and methods, averaged over all allowed and injected missing thresholds. Rice data are reported averaged by chromosome and on the complete genotypes. Alfalfa data are reported averaged over the two Alfalfa-PV and Alfalfa-Med populations. FILLIN failed to impute alfalfa datasets.}
\label{tab:accuracy_statistics}
\begin{tabular}{llcccc}
\hline\noalign{\smallskip}
\noalign{\smallskip}\hline\noalign{\smallskip}
\textbf{Dataset} & \textbf{Method} & \textbf{Total} & \textbf{Minor (BB)} & \textbf{Major (AA)} & \textbf{Heterozygote (AB)}\\
\noalign{\smallskip}\Xhline{3\arrayrulewidth}\noalign{\smallskip}
alfalfa & Beagle & 73.14 & 14.27 & 99.37 & 20.77\\
alfalfa & Beagle (shuffle) & 66.34 & 1.31 & 99.88 & 0.50\\
alfalfa & kNNI & 82.20 & 14.68 & 90.82 & 66.03\\
alfalfa & MNI & 78.38 & 0.00 & 88.69 & 58.88\\
alfalfa & RFI  & 79.50 & 0.01 & 89.05 & 61.75\\
alfalfa & SVDI & 77.36 & 4.47 & 85.81 & 61.67\\
alfalfa & FILLIN & * & * & * & *\\
alfalfa & FILLIN (shuffle)  & * & * & * & *\\
rice (chr) & Beagle & 99.58 & 97.50 & 99.80 & -\\
rice (chr) & Beagle (shuffle) & 96.09 & 74.73 & 98.42 & -\\
rice (chr) & kNNI & 98.10 & 89.12 & 99.04 & -\\
rice (chr) & MNI & 90.19 & 1.06 & 99.89 & -\\
rice (chr) & RFI  & 98.81 & 91.51 & 99.58 & -\\
rice (chr) & SVDI & 97.81 & 85.64 & 99.11 & -\\
rice (chr) & FILLIN & 86.96 & 63.62 & 90.14 & -\\
rice (chr) & FILLIN (shuffle)  & 82.19 & 55.86 & 85.81 & -\\
rice & Beagle & 99.58 & 97.57 & 99.80 & -\\
rice & Beagle (shuffle) & 93.48 & 55.64 & 97.69 & -\\
rice & kNNI & 98.30 & 89.80 & 99.19 & -\\
rice & MNI & 90.21 & 0.61 & 99.89 & -\\
rice & RFI  & 97.86 & 84.68 & 99.28 & -\\
rice & SVDI & 95.74 & 70.96 & 98.40 & -\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

@@

\bibliographystyle{spmpsci}

\end{document}
